Cor Compare

### 2022-09-26 graphs_newt_snakes/corcompare.Rmd
looking at the cor data in more depth

GA1_cor_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor.txt" , header = TRUE)
GA1_cor_tall_file$group_rep <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd, "_", GA1_cor_tall_file$rep)
GA1_cor_tall_file$group <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd)
GA1_cor_tall_file$sim=LETTERS[factor(GA1_cor_tall_file$group)]
GA1_cor_tall_file$experiment = "A"

GA1_cor_tall_7_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor_7.txt" , header = TRUE)
GA1_cor_tall_7_file$group_rep <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd, "_", GA1_cor_tall_7_file$rep)
GA1_cor_tall_7_file$group <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd)
GA1_cor_tall_7_file$sim=LETTERS[factor(GA1_cor_tall_7_file$group)]
GA1_cor_tall_7_file$experiment = "B"

her_cor_tall_file<- read.csv("~/Desktop/no_hair/all_cor.txt", header = TRUE)
her_cor_tall_file$group_rep <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd, "_", her_cor_tall_file$rep)
her_cor_tall_file$group <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd)
her_cor_tall_file$sim=LETTERS[factor(her_cor_tall_file$group)]
her_cor_tall_file$experiment = "C"

@@

all_cor_exp = rbind(GA1_cor_tall_file, GA1_cor_tall_7_file, her_cor_tall_file, inter_cor_tall_file)

all_cor_exp$group_exp=paste0(all_cor_exp$group, "_", all_cor_exp$experiment)

@@

  return(plot)
}
```

@@

>>>>

GA1_cor_tall_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor.txt" , header = TRUE)
GA1_cor_tall_file$group_rep <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd, "_", GA1_cor_tall_file$rep)
GA1_cor_tall_file$group <- paste0(GA1_cor_tall_file$snake_mu_rate, "_", GA1_cor_tall_file$snake_mu_effect_sd,"_",GA1_cor_tall_file$newt_mu_rate, "_", GA1_cor_tall_file$newt_mu_effect_sd)
GA1_cor_tall_file$sim=LETTERS[factor(GA1_cor_tall_file$group)]
GA1_cor_tall_file$experiment = "A"
toDelete <- seq(2, nrow(GA1_cor_tall_file), 2)
GA1_cor_tall_file_even = GA1_cor_tall_file[-toDelete,]

GA1_cor_tall_7_file<- read.csv("~/Desktop/GA1_tall_redo/all_cor_7.txt" , header = TRUE)
GA1_cor_tall_7_file$group_rep <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd, "_", GA1_cor_tall_7_file$rep)
GA1_cor_tall_7_file$group <- paste0(GA1_cor_tall_7_file$snake_mu_rate, "_", GA1_cor_tall_7_file$snake_mu_effect_sd,"_",GA1_cor_tall_7_file$newt_mu_rate, "_", GA1_cor_tall_7_file$newt_mu_effect_sd)
GA1_cor_tall_7_file$sim=LETTERS[factor(GA1_cor_tall_7_file$group)]
GA1_cor_tall_7_file$experiment = "B"
toDelete <- seq(2, nrow(GA1_cor_tall_7_file), 2)
GA1_cor_tall_7_file_even = GA1_cor_tall_7_file[-toDelete,]

her_cor_tall_file<- read.csv("~/Desktop/no_hair/all_cor.txt", header = TRUE)
her_cor_tall_file$group_rep <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd, "_", her_cor_tall_file$rep)
her_cor_tall_file$group <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd)
her_cor_tall_file$sim=LETTERS[factor(her_cor_tall_file$group)]
her_cor_tall_file$experiment = "C"
toDelete <- seq(2, nrow(her_cor_tall_file), 2)
her_cor_tall_file_even = her_cor_tall_file[-toDelete,]

@@

all_cor_exp = rbind(GA1_cor_tall_file_even, GA1_cor_tall_7_file_even, her_cor_tall_file_even, inter_cor_tall_file)

all_cor_exp$group_exp=paste0(all_cor_exp$group, "_", all_cor_exp$experiment)
all_cor_exp$exp_group=paste0(all_cor_exp$experiment, "_", all_cor_exp$group)

@@

counting_threshold <- function(file, treshold, whichgroup, p_n_b, min_gen, max_gen){

  file=file[which(file$gen>=min_gen & file$gen<=max_gen),]

  if(p_n_b == "p"){
  table <-  file %>%
  group_by(get(whichgroup)) %>%
  tally(mean_newt_pheno_By_mean_snake_pheno >= treshold)
  return(table)
  }

  if(p_n_b == "n"){
  table <-  file %>%
  group_by(get(whichgroup)) %>%
  tally(mean_newt_pheno_By_mean_snake_pheno <= -treshold)
  return(table)
  }

  if(p_n_b == "b"){
  table <-  file %>%
  group_by(get(whichgroup)) %>%
  tally(mean_newt_pheno_By_mean_snake_pheno <= -treshold | mean_newt_pheno_By_mean_snake_pheno >= treshold)
  return(table)
  }else{
    print("p_n_b needs to be positive, negative, or both (p, n, or b)")
  }

}
```

@@

```{r, thresholds}

file = all_cor_exp
treshold = 0.3
p_n_b = "p"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)

file = all_cor_exp
treshold = 0.3
p_n_b = "b"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)

file = all_cor_exp
treshold = 0.5
p_n_b = "b"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)

file = all_cor_exp
treshold = 0.7
p_n_b = "b"
min_gen = 100
max_gen =50000
whichgroup = "experiment"

counting_threshold(file, treshold, whichgroup, p_n_b, min_gen, max_gen)

file = all_cor_exp
treshold = 0.7
p_n_b = "b"
min_gen = 100
max_gen =50000
whichgroup = "experiment"
```

```{r, distribuuution plots, fig.height = 11, fig.width = 5}

dummy<-all_cor_exp %>%
  group_by(group_exp) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)

ggplot(all_cor_exp[which(all_cor_exp$gen>=min_gen & all_cor_exp$gen<=max_gen),])+
   #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  #xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=mean_newt_pheno_By_mean_snake_pheno, fill=experiment))+ #, y=threshold
 # theme(plot.title = element_text(size=5)) +
 # xlim(-.1, 1.1)+
  #geom_vline(data = dummy, aes(xintercept = name))+
  facet_grid(group~experiment)+
  #facet_wrap(~group_exp)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                    strip.background = element_blank(), strip.text.x = element_blank(),
                   title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                    axis.title.y = element_blank())
```

```{r, other plots}
dummy<-all_cor_exp %>%
  group_by(experiment) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)

ggplot(all_cor_exp[which(all_cor_exp$gen>=min_gen & all_cor_exp$gen<=max_gen),])+
   #ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen"))+
  #xlab(x_label) + ylab(y_label)+
  geom_histogram(aes(x=mean_newt_pheno_By_mean_snake_pheno, fill=experiment))+ #, y=threshold
 # theme(plot.title = element_text(size=5)) +
 # xlim(-.1, 1.1)+
  geom_vline(data = dummy, aes(xintercept = name))+
  facet_wrap(~experiment)+
  theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8),
                    strip.background = element_blank(), strip.text.x = element_blank(),
                   title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                    axis.title.y = element_blank())
